WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-24 ms.tex
Remove Barankin bound, won't be using it
Correct sign of iwt
Why just ML estimates?

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} point estimates of the signal parameters are
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_i, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{-i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{-i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega.
\end{eqnarray}

@@

@@

\subsection{Barankin bound}

It is well known that the \ac{CRLB} is not a tight bound in the sense that there does not always exist an estimator that achieves it. Barankin derived a tight bound for any unbiased estimator \cite{barankin1949locally}.

>>>>

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} point estimates of the signal parameters are
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_\mathrm{in}, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega.
\end{eqnarray}
%
A detection candidate consists of the set $\{\hat{\boldsymbol\theta}_\mathrm{in}, \left\{ \hat\rho_i, \hat\gamma_i, \hat\tau_i \right\}_i\}$. There are various ways to characterize the significance of a
detection candidate, but in Gaussian noise the combined SNR $\hat\rho_\mathrm{c}$ suffices,
%
\marginpar{What is the least that I can get away with saying about false alarm rate estimation and likelihood ratios?}
%
\begin{equation}
	\hat\rho_\mathrm{c} = \sqrt{\sum_i {\hat\rho_i}^2}.
\end{equation}.

@@

For the purpose of rapid sky localization, we assume that we do not have access to the \ac{GW} data $\mathbf{x}$ itself, and that our only contact with it is through the ML parameter estimates $\{\hat{\boldsymbol\theta}_\mathrm{in}, \left\{ \hat\rho_i, \hat\gamma_i, \hat\tau_i \right\}_i\}$. Although this is a significant departure from conventional GW parameter estimation techniques, we can still apply the full Bayesian machinery of Equation~(\ref{eq:marginal-posterior}) to compute a posterior distribution for the sky location.

\marginpar{This is poorly worded.}%
%
There are many practical advantages of doing so. For one, there are difficulties in synchronously gathering together the calibrated GW strain data, auxiliary instrument channels, and data quality vetoes from all of the sites. The data consumed by the real\nobreakdashes-time detection pipeline are not necessarily final. Longer\nobreakdashes-running follow\nobreakdashes-up analyses can benefit from offline calibration, whereas the rapid sky localization need not re\nobreakdashes-analyze the online data.

Moreover, the dimensionality of the problem is greatly reduced, and the problem becomes computationally easier.

@@
